\begin{enumerate}
    \itemsep0em 
    \item P.A. Petrosyan, H.H. Khachatrian, Further results on the deficiency of graphs, Discrete Applied Mathematics, 2017, http://dx.doi.org/10.1016/j.dam.2017.04.005.
    \item H.H. Khachatrian, Deficiency of outerplanar graphs, Proceedings of the Yerevan State University. Physical and Mathematical Sciences, 2017, 51 (1), pp. 22-28.
    \item H.H. Khachatrian, P.A. Petrosyan, Interval edge-colorings of complete graphs, Discrete Mathematics 339, 2016, pp. 2249-2262.
    \item P.A. Petrosyan, H.H. Khachatrian, T.G. Mamikonyan, On interval edge-colorings of bipartite graphs, 2015 Computer Science and Information Technologies (CSIT), Yerevan, 2015, pp. 71-76.
    \item H.H. Khachatrian, P.A. Petrosyan, Interval edge-colorings of Hamming graphs, 8th Slovenian Conference on Graph Theory, Kranjska Gora, Slovenia, 2015, p. 134.
    \item P.A. Petrosyan, H.H. Khachatrian, Interval non-edge-colorable bipartite graphs and multigraphs, Journal of Graph Theory 76, Issue 3, 2014, pp. 200-216.
    \item A. Grzesik, H.H. Khachatrian, Interval edge-colorings of $K_{1,m,n}$, Discrete Applied Mathematics 174, 2014, pp. 140-145.
    \item H.H. Khachatrian, P.A. Petrosyan, Interval edge-colorings of complete graphs, 7th Cracow Conference on Graph Theory, Rytro, Poland, 2014, pp. 35-36.
    \item A. Grzesik, H.H. Khachatrian, P.A. Petrosyan, On interval edge-colorings of complete multipartite graphs, 5th Polish Combinatorial Conference, Bedlewo, Poland, 2014, p. 29.
    \item P.A. Petrosyan, H.H. Khachatrian, H.G. Tananyan, Interval edge-colorings of Cartesian products of graphs I, Discussiones Mathematicae Graph Theory 33(3), 2013, pp. 613-632.
    \item A. Grzesik, H. Khachatrian, On interval edge-colorings of complete tripartite graphs, 9th International Conference on Computer Science and Information Technologies, Revised Selected Papers, Yerevan, 2013, pp. 1-3.
    \item P.A. Petrosyan, H.H. Khachatrian, On a generalization of interval edge colorings of graphs, 15th Workshop on Graph Theory, Colourings, Independence and Domination, Szklarska Poreba, Poland, 2013, p. 44.
    \item P.A. Petrosyan, H.H. Khachatrian, H.G. Tananyan, Interval edge-colorings of Cartesian products of graphs, 14th Workshop on Graph Theory, Colourings, Independence and Domination, Szklarska Poreba, Poland, 2011, p. 44.
    \item P.A. Petrosyan, H.H. Khachatrian, L.E. Yepremyan, H.G. Tananyan, Interval edge-colorings of graph products, Proceedings of the CSIT Conference, Yerevan, 2011, pp. 89-92.
    \item П.А. Петросян, Г.А. Хачатрян, Интервальные реберные раскраски декартовых произведений регулярных графов, Пятая годичная научная конференция РАУ (Сборник научных работ), 2010, стр. 241-248.
\end{enumerate}